Vagueness, Noise, and Signaling

### 2015-01-18 paper/version_02/paper.tex
Removed reference to Sainsbury and Keefe.

This outline of an approach to categorization using sim-max games
leaves many problems unaddressed. One of them is that natural
categories for continuously variable stimuli usually do not have
unique, point-valued prototypes and clear category boundaries. We
would like to account for the possibility of such vagueness, in
particular: (i) clear positive examples of a vague category should
show a gradient transition to clear negative examples;
(ii) prototypes should likewise be gradient regions, peaking at the
center of the vague category they represent
\citep[e.g.][]{Sainsbury1991:Is-There-Higher,KeefeSmith1997:Vagueness:-A-Re}.\todo{check
  whether references are okay/appropriate in this context}

>>>>

This outline of an approach to categorization using sim-max games
leaves many problems unaddressed. One of them is that natural
categories for continuously variable stimuli usually do not have
unique, point-valued prototypes and clear category boundaries. We
would like to account for the possibility of such vagueness, in
particular: (i) clear positive examples of a vague category should
show a gradient transition to clear negative examples;
(ii) prototypes should likewise be gradient regions, peaking at the
center of the vague category they represent.
